---
title: "Visual Feedback and The Two-Rate Model"
output: html_notebook
---

This notebook will allow you to download the necessary data from OSF and compute some stats and make the corresponding plots to those analysis. 

```{r echo=FALSE}
source('R/shared.R')
source('R/Figures.R')
source('R/Analysis.R')
source('R/asymptoticDecayModel_terminal.R')
source('R/Repeated_Measures_Combine.R')
downloadOSFdata()
loadalldata()
loadcolors()
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

```{r plots}
Reachmodel(passive_reaches, 'Passive', condition = 'loc', loc_data = passive_localization, color = colorPA)
Reachmodel(terminal_reaches, 'Terminal', condition = 'loc', loc_data = terminal_localization, color = colorT)
svglite('figs/Manuscript Figures_Jan19.svg', width = 12, height = 8, system_fonts=list(sans = "Arial"))
layout(matrix(c(1,2,3,4), nrow = 2, byrow = TRUE))
neuromatchReaches()
mtext('a', outer=FALSE, side=3, las=1, line=1, adj=0, padj=1,cex = 2.5)
plotREAANOVA()
mtext('b', outer=FALSE, side=3, las=1, line=1, adj=0, padj=1,cex = 2.5)
Localizations(passive_localization, terminal_localization, exposure_localization)
mtext('a', outer=FALSE, side=3, las=1, line=1, adj=0, padj=1,cex = 2.5)
plotpassiveprop4points()
mtext('b', outer=FALSE, side=3, las=1, line=1, adj=0, padj=1,cex = 2.5)
dev.off()

svglite('figs/Schedule.svg', width = 6, height = 2, system_fonts=list(sans = "Arial"))
Plotschedule(passive_reaches)
dev.off()


```


```{r Analysis}
library(ez)
ANOVAdata<- PrepdataforANOVA(passive_reaches,terminal_reaches)
ReachANOVA<-ANOVAanalysis(ANOVAdata)
leveneTest(Deviations~Time, ANOVAdata)
leveneTest(Deviations~Experiment, ANOVAdata)
ReachANOVA
Ttestdata<- PrepdataforT(passive_reaches,terminal_reaches)
tanalyzedata(Ttestdata)

Rebounds<- PrepANOVARebounds(passive_reaches,terminal_reaches,exposure_reaches)
leveneTest(EC_Late~Experiment, Rebounds)
oneway.test(EC_Late~Experiment, Rebounds,na.action = na.omit, var.equal = FALSE)
#inconclusive
equivalence()
anovaBF(EC_Late~Experiment, Rebounds)

ttestBF(Rebounds$EC_Late[Rebounds$Experiment == 'Passive'], Rebounds$EC_Late[Rebounds$Experiment == 'Terminal'], paired = FALSE)
ttestBF(Rebounds$EC_Late[Rebounds$Experiment == 'Exposure'], Rebounds$EC_Late[Rebounds$Experiment == 'Terminal'], paired = FALSE)
ttestBF(Rebounds$EC_Late[Rebounds$Experiment == 'Passive'], Rebounds$EC_Late[Rebounds$Experiment == 'Exposure'], paired = FALSE)

Implicit<-Reboundanalysis(Rebounds)
Implicit


ANOVAPdata<- PrepdataforPropANOVA(passive_localization, terminal_localization, exposure_localization)
TtestPdata<- PrepdataforPropT(passive_localization, terminal_localization, exposure_localization)

LocANOVA<-ANOVAanalysis(ANOVAPdata)
LocANOVA

##Reach Model Comparison
Passive_metrics<- GroupModelAICs(passive_reaches, 'Passive')
Terminal_metrics<- GroupModelAICs(terminal_reaches, 'Terminal')
Runlogregression()


##Rate of Change
bootstrapSemiAsymptoticDecayModels()
getAsymptoticDecayParameterCIs()
getSaturationTrials()


#Fast process comparison between terminal and continuous
parsforttest<-ParticipantReachmodels2(passive_reaches, terminal_reaches)
t.test(parsforttest$Rf[parsforttest$Experiment == "Continuous"],parsforttest$Rf[parsforttest$Experiment == "Terminal"]) 
cohen.d(parsforttest$Rf[parsforttest$Experiment == "Continuous"],parsforttest$Rf[parsforttest$Experiment == "Terminal"], na.rm = TRUE)
etaSquaredTtest(parsforttest$Rf[parsforttest$Experiment == "Continuous"],parsforttest$Rf[parsforttest$Experiment == "Terminal"], na.rm = TRUE)
t.test(parsforttest$Lf[parsforttest$Experiment == "Continuous"],parsforttest$Lf[parsforttest$Experiment == "Terminal"]) 
cohen.d(parsforttest$Lf[parsforttest$Experiment == "Continuous"],parsforttest$Lf[parsforttest$Experiment == "Terminal"], na.rm = TRUE)
etaSquaredTtest(parsforttest$Lf[parsforttest$Experiment == "Continuous"],parsforttest$Lf[parsforttest$Experiment == "Terminal"], na.rm = TRUE)




```


```{r}
RegressionPLot()
plotpropmodels()


plotfitPropModel(terminal_reaches, terminal_localization, colorT, 'Terminal Prop Model')
plotfitPropModel(passive_reaches, passive_localization, colorPA, 'Continuous Prop Model')
plotfitPropModel(exposure_reaches, exposure_localization, colorE, 'Exposure Prop Model', exp = 'exp')
dev.off()
Passive_PropMetrics<-LocalizationModelCompare(passive_localization, passive_reaches, colorPA)
Active_PropMetrics<-LocalizationModelCompare(active_localization, active_reaches, colorA)
Exposure_PropMetrics<-ExpoLocalizationModelCompare(exposure_localization, exposure_reaches, colorE)
Terminal_PropMetrics<-LocalizationModelCompare(terminal_localization, terminal_reaches, colorT)
```
